\textbf{3D Multisystemic Finite Element Model of the Chinchilla Inner Ear}

### 2021-06-28 paper.tex
6-28-21

\title{\textbf{3D Finite Element Model of the Chinchilla Inner Ear for Analysis of Multisystemic Pathologies}}
\author{Nicholas Castle$^1$ \and Junfeng Liang$^1$\and Ke Zhang$^2$\and Chenkai Dai$^{12}$}
\institute{$^1$School of Aerospace and Mechanical Engineering \\ $^2$Stephenson School of Biomedical Engineering \\ University of Oklahoma, Norman OK 73019}

@@

Edit this as the model is completed and material properties are applied

@@

@@

\subsection{FE Analysis}
NEED \newline - Graph from FE analysis like seen in Junfengs paper
- Maybe a figure showing the allocation of material properties by color

@@

   The greatest effect of the vestibular system and cochlea on the other can be predictably seen at the base of the cochlea and the utricular and saccular vestibules as they are the closest in proximity to one another.  Studies with rodents have confirmed this effect \cite{mizrachi}

Geometric accuracy of the vestibular system and cochlea will allow for studies into the effects of numerous diseases of the inner ear by varying geometry and applying further inverse finite element analysis to compare with data recieved from both human and chinchilla tests subjects. These studies can include the effects of otitis media, inflammation of inner ear tissues, and genetic abnormalities.

 Because the saccule is linked to the cochlear duct, propagation of waves due to angular motion of the SCC’s can cause perturbations of the base of the cochlea resulting in sensible alterations in hearing, with intense noises capable of producing a similar effect in the vestibular system. For this reason, it is vital that the membranous labyrinth be modeled in its entirety, linking the saccule and the ductus cochlearis with the canalus reuniens and allowing for analysis of their effects on one another.

Completed nerve, temporal bone, and auditory cortex geometries can be substituted into the model as needed later to allow for analysis of multisystemic pathologies which are the result of both mechanical and electrical malfunctions in the ear. The accuracy of geometry in nervous tissue will allow for studies on the effect of procedures or implants on nerve function. One example is that of the installation of a cochlear implant, where electrodes could be optimized through reverse analysis of the finite element model and allow for new technologies which minimize the effect on face or tongue feeling.

Some features that are important for vestibulocochlear function have been omitted and their inclusion could improve results in the future. These include the finer details of the organ of corti, the ductus cochlearis, the tectorial membrane and reticular lamina. These features would allow for more accurate analysis of the mechanics of the basilar membrane. Another valuable addition would be the involvment of a seperate finite element model representing a sensory hair cell. This would make transient analysis of multisystemic pathologies feasible by translating deflection from the mechanical model into electrical impulses which could be studied in the electrical model. \cite{choi} Inclusion of the temporal bone will allow for studies on the effects of concussive blasts and provide an opportunity for analysis of the inner ear in its damaged state. The direct relationship between hearing and balance has been found to be significant JUNFENG PAPER and is one that merits further study.

>>>>

\title{\textbf{3D Multisystemic Finite Element Model of the Chinchilla Inner Ear}}
\author{Nicholas Castle$^1$ \and Junfeng Liang$^1$\and Ke Zhang$^2$\and Chenkai Dai$^{12}$}
\institute{$^1$School of Aerospace and Mechanical Engineering \\ $^2$Stephenson School of Biomedical Engineering \\ University of Oklahoma, Norman OK 73019}

@@

Edit this as the model is completed and material properties are applied
Include a large table of all material properties and their origins

@@

-Get help from Junfeng on this part, not sure what else to include here

@@

\subsection{FE Analysis}
NEED \newline - Graph from FE analysis like seen in Junfengs paper
- Maybe a figure showing the allocation of material properties by color
- Will have graphs/images for each trial, acoustic harmonic and 2 accelerations
- Reference Junfeng and Gans papers to word and report important values
- Get Junfengs help on this part

@@

Because the saccule is linked to the cochlear duct, propagation of waves due to angular motion of the SCC’s can cause perturbations of the base of the cochlea resulting in sensible alterations in hearing, with intense noises capable of producing a similar effect in the vestibular system. For this reason, it is vital that the membranous labyrinth be modeled in its entirety, linking the saccule and the ductus cochlearis with the canalus reuniens and allowing for analysis of their effects on one another. The greatest effect of the vestibular system and cochlea on the other can be predictably seen at the base of the cochlea and the utricular and saccular vestibules as they are the closest in proximity to one another. INSERT SOME REFERENCES TO OUR DATA HERE.  Studies with rodents have confirmed this effect \cite{mizrachi}

DISCUSSION ON RESULTS FROM MACULAE, CUPULAS

Geometric accuracy of the vestibular system and cochlea will allow for studies into the effects of numerous diseases of the inner ear by varying geometry and applying further inverse finite element analysis to compare with data recieved from both human and chinchilla tests subjects. These studies can include the effects of otitis media, inflammation of inner ear tissues, and genetic abnormalities. Completed nerve, temporal bone, and auditory cortex geometries can be substituted into the model as needed later to allow for analysis of multisystemic pathologies which are the result of both mechanical and electrical malfunctions in the ear. The accuracy of geometry in nervous tissue will allow for studies on the effect of procedures or implants on nerve function. One example is that of the installation of a cochlear implant, where electrodes could be optimized through reverse analysis of the finite element model and allow for new technologies which minimize the effect on face or tongue feeling. Inclusion of the temporal bone will allow for studies on the effects of concussive blasts and provide an opportunity for analysis of the inner ear in its damaged state.

This model is also capable of being attached to a developed model of the chinchilla middle and outer ear. After the behaviour of this inner ear model is concretely known the middle ear transfer function in various scenarious can be recorded to aid clinical diagnosis of ear disorders.

Some features that are important for vestibulocochlear function have been omitted and their inclusion could improve results in the future. Imaging was unable to capture the proper thicknesses of many membranes on its own. This could be improved using histology, OCR scanning technology, and mechanical testing of excised tissues from recently diceased animal specimens to ensure the proper elasticity and water content of the tissue. Another valuable addition would be the involvement of a seperate finite element model representing a sensory hair cell. This would make transient analysis of multisystemic pathologies feasible by translating deflection from the mechanical model into electrical impulses which could be studied in the electrical model. \cite{choi}
